---
title: "pre_run"
author: "Ziqi Zhou"
date: "3/12/2020"
output: pdf_document

\fontsize: 11
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(caret)
library(MASS)

library(splines)
library(mgcv)
library(ggplot2)
library(patchwork)
library(pdp)
library(earth)
library(corrplot)
library(plotmo)

library(mlbench)

library(e1071)
```

# Introduction

The red wine is one of the most popular alcoholic beverages in the world. Most of our team members enjoy drinking red wine and have a great interest in factors that can affect the quality of the red wine. We want to figure out what determined the quality of the wine. Based on this motivation, we choose this dataset “Red Wine Quality”.

This dataset has 12 columns and 1599 rows. And after omitting the NA data, we still got 1599 rows which means there is no missing value in this dataset.

Variable introduction
1. fixed acidity : most acids involved with wine or fixed or nonvolatile (do not evaporate readily)
2.volatile acidity : the amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste
3.citric acid : found in small quantities, citric acid can add 'freshness' and flavor to wines
4.residual sugar : the amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with greater than 45 grams/liter are considered sweet
5.chlorides : the amount of salt in the wine
6.free sulfur dioxide : the free form of SO2 exists in equilibrium between molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial growth and the oxidation of wine
7.total sulfur dioxide : amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine
8.density : the density of water is close to that of water depending on the percent alcohol and sugar content
9.pH : describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale
10.sulphates : a wine additive which can contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial and antioxidant
11.alcohol : the percent alcohol content of the wine
12.quality (response): output variable (based on sensory data, score between 0 and 10)
    
    
We would like to know what factors influence the quality of the wine and try to build a model to predict the quality of wine given the specific factors.
    
I used the code below to prepare and clean the data.

```{r,include=FALS,Emessage = FALSE, warning=FALSE}
#read data and omit missing value
wine = read_csv("./data/winequality-red.csv") %>% 
  janitor::clean_names() %>% 
  na.omit() 
```

```{r}
# Separate data into training data and test data
set.seed(11)
trRows = createDataPartition(wine$quality, p = .75, list = F)

#all data
x = model.matrix(quality ~ .,wine)[,-1]
y = wine$quality

# Training data
x1 = model.matrix(quality ~ .,wine)[trRows,-1]
y1 = wine$quality[trRows]

# test data
x2 = model.matrix(quality ~ .,wine)[-trRows,-1]
y2 = wine$quality[-trRows]
```

```{r include=FALSE}
#set ctrl1
ctrl1 <- trainControl(method = "cv", number = 10)
```

# Exploratory Data Analysis


```{r, fig.height=4, echo = FALSE}
f_a = ggplot(wine,aes(x =fixed_acidity)) + 
  geom_density()

v_c = ggplot(wine,aes(x =volatile_acidity)) + 
  geom_density()

c_a = ggplot(wine,aes(x =citric_acid)) + 
  geom_density()

r_s = ggplot(wine,aes(x =residual_sugar)) + 
  geom_density()

chol = ggplot(wine,aes(x =chlorides)) + 
  geom_density()

fsd = ggplot(wine,aes(x =free_sulfur_dioxide)) + 
  geom_density()

tsd = ggplot(wine,aes(x =total_sulfur_dioxide)) + 
  geom_density()

denst = ggplot(wine,aes(x =density)) + 
  geom_density()

ph = ggplot(wine,aes(x =p_h)) + 
  geom_density()

sup = ggplot(wine,aes(x =sulphates)) + 
  geom_density()

achol = ggplot(wine,aes(x =alcohol)) + 
  geom_density()

(f_a + v_c + c_a + r_s + chol) / (fsd + tsd + denst + ph + sup + achol)

```


```{r, fig.height=4}
#Create scatter plots of responses and predictors
theme1 <- trellis.par.get()
theme1$plot.symbol$col <- rgb(.2, .4, .2, .5)
theme1$plot.symbol$pch <- 16
theme1$plot.line$col <- rgb(.8, .1, .1, 1)
theme1$plot.line$lwd <- 2
theme1$strip.background$col <- rgb(.0, .2, .6, .2)
trellis.par.set(theme1)
featurePlot(x, y, plot = "scatter", labels = c("","Y"),
            type = c("p"), layout = c(4, 2))
```

```{r fig.height=4}
corrplot(cor(x1), method = "square", type = "full")
```
**description**
positive correlation negative correlation
pH and fixed acidity
alcohol and density
citric acid and fixed acidity
citric acid and volatile acidity

# Models

**But we cannot use test error to choose model.**
**However we could report the test error of the final model**

```{r}
#linear fit R^2 = 0.3458
set.seed(11)
lm.fit <-train(x1, y1,method = "lm",
               trControl = ctrl1)
summary(lm.fit)
```

```{r}
#Ridge fit
set.seed(11)
ridge.fit <-train(x1, y1,method = "glmnet",
                  tuneGrid =expand.grid(alpha = 0,
                                        lambda =exp(seq(-5, 5, length=100))),
                  trControl = ctrl1)
                
plot(ridge.fit, xTrans =function(x)log(x))
ridge.fit$bestTune
coef(ridge.fit$finalModel,ridge.fit$bestTune$lambda)

#test error
predict_y_ridge = predict(ridge.fit, s = ridge.fit$bestTune, newdata = x2)
mse_ridge = mean((y2-predict_y_ridge)^2)
```

```{r}
set.seed(11)
# Lasso
lasso.fit = train(x1, y1,method = "glmnet",
                  tuneGrid =expand.grid(alpha = 1,
                                        lambda =exp(seq(-10, 0, length=100))),
                  trControl = ctrl1)
summary(lasso.fit)              
plot(lasso.fit, xTrans =function(x)log(x))
lasso.fit$bestTune
coef(lasso.fit$finalModel,lasso.fit$bestTune$lambda)

#test error
predict_y_lasso = predict(lasso.fit, s = lasso.fit$bestTune, newdata = x2)
test_error_lasso = mean((y2-predict_y_lasso)^2)
```

```{r}
#pcr
set.seed(11)
pcr.fit <-train(x1, y1,
                method = "pcr",
                tuneGrid  =data.frame(ncomp = 1:11),
                trControl = ctrl1,
                preProc =c("center", "scale"))

ggplot(pcr.fit, highlight = TRUE) +theme_bw()
# so the ncomp = 11
#pcr.fit$finalModel$coefficients
```
, , 11 comps

                         .outcome
fixed_acidity        -0.046151690
volatile_acidity     -0.207362623
citric_acid          -0.044630750
residual_sugar       -0.006087958
chlorides            -0.105520584
free_sulfur_dioxide   0.059433323
total_sulfur_dioxide -0.134563961
density               0.045446567
p_h                  -0.101488031
sulphates             0.151034045
alcohol               0.324604503
```{r}
#pls
set.seed(11)
pls.fit <-train(x1, y1,method = "pls",
                tuneGrid =data.frame(ncomp = 1:12),
                trControl = ctrl1,preProc =c("center", "scale"))

predy2.pls2 <-predict(pls.fit, newdata = x2)


ggplot(pls.fit, highlight = TRUE)
```

Treat the response quality as continous variable or classified variable
How to treat quality as classified variable? factor the response


```{r, fig.height=4}
#fit GAM
set.seed(11)
gam.fit <- train(x1, y1,
                 method = "gam",
                 tuneGrid = data.frame(method = "GCV.Cp", select = FALSE),
                 trControl = ctrl1)
summary(gam.fit)
gam.fit$finalModel

plot(gam.fit$finalModel)

```


```{r}
# MARS 
mars_grid <- expand.grid(degree = 1:2, 
                         nprune = 1:12)

set.seed(11)
mars.fit <- train(x1, y1,
                  method = "earth",
                  tuneGrid = mars_grid,
                  trControl = ctrl1)

ggplot(mars.fit)

summary(mars.fit)

mars.fit$bestTune
coef(mars.fit$finalModel) 
```



Look R-squared

MSE

## Resample

```{r}
resamp = resamples(list(lm = lm.fit, ridge = ridge.fit, lasso = lasso.fit, mars = mars.fit, gam = gam.fit, pcr = pcr.fit, pls = pls.fit))

summary(resamp)
bwplot(resamp, metric = "RMSE")
```



What predictor include

Model fitting method. assumptions. Treat the response as continous variable.

tuning parameter there is no tuning parameter

training test ( MSE?)
 which var plays important role
 
limitation classification just treat response as continous we could do more
flexible?








